\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[left=3.5cm, right=3.5cm]{geometry}

\title{Minutes of meeting \#1}
\author{Group 6}
\date{Tuesday, 2018-02-06 12:15-14:00}

\begin{document}
\maketitle

\section{Attendance}
\begin{tabular}{l l}
    Benjamin Dyhre Bjønnes     & present \\
    Robin el Salim             & present \\
    Sverre Magnus Engø         & present \\
    Robin Grundvåg             & present \\
    Vegard Itland              & present \\
    Eirik Jørgensen            & present \\
    Loc Tri Le                 & present \\
    Stian Soltvedt             & present
\end{tabular}

\section{Pre-meeting catchup}

Since this was the first meeting, there is no catchup.

\section{Main topic: Team organization (subtask \#1)}

\paragraph{Splitting the teams}

We split the teams along the long axis of the table, since people who wished to work together were naturally clustered together. From here on, any references to "the group" or "the team" will be referencing Group 6 unless otherwise specified.

\paragraph{Assigning roles (first draft)}

Please note that these roles may be subject to change, and more roles will be added as necessary. Unassigned team members are currently considered as "free resources" which may take on necessary tasks.\newline

\begin{tabular}{l l l}
    Name                       & Role              & Comment \\
    \hline
    Benjamin Dyhre Bjønnes     &                   & \\
    Robin el Salim             &                   & \\
    Sverre Magnus Engø         & team leader       & most experienced in collaborations \\
    Robin Grundvåg             &                   & \\
    Vegard Itland              & doc. manager      & transcribes minutes of meeting, \\
                               &                   & responsible for documentation \\
    Eirik Jørgensen            &                   & \\
    Loc Tri Le                 &                   & \\
    Stian Soltvedt             & git repo manager  & highly experienced git user
\end{tabular}

\newpage
\paragraph{Communication}

The group decided on communicating using Facebook Messenger. A group chat was established for this purpose.

\paragraph{Physical meetings}

We decided on an additional weekly meeting outside of the group sessions every Tuesday. The meeting is currently scheduled to be held on Thursday at 14:15-16:00. The location of the second meeting has not been decisively decided, but for the time being we intend to try holding our next meeting in a room in Høyteknologisenteret.

\paragraph{Languages}

The working language will mainly be Norwegian (oral communication, Facebook chat). Deliverables will be written in English, and future code will use English naming schemes. The project will most likely be implemented using Java, due to it being the programming language with which the group is most broadly experienced.

For the time being, the minutes of meeting and other notes will be written using Markdown or alternative formats due to the simplicity compared to fully formatted LaTeX documents. The documents will later be transcribed to LaTeX and exported as PDF files.

\paragraph{Tools}

\subparagraph{Git and GitLab}

A de-facto policy of using the syntax "[Affected file] change description" or "[Topic] content description" in commit message titles has been adopted. Furthermore, a de-facto policy of pushing meeting notes directly to the master branch has taken effect. This policy will be subject to review and a high probability of change in later meetings.

\subparagraph{Trello}

A Trello project has been established. Some preliminary tasks related to the second obligatory assignment have been added. The precise usage of this tool is a topic for further discussion.

\section{Conclusion}

We mainly discussed the organization of our team and how we will work from here on. We've also touched on topics such as the use of languages and tools, and assigned roles to some of the team members. Most of the decisions described in this document may be subject to change.

\paragraph{Next meeting}

The next meeting will be held in Høyteknologisenteret on Thursday 2018-02-13 at 14:15-16:00.

\end{document}
