\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[left=3.5cm, right=3.5cm]{geometry}
\usepackage[sharp]{easylist}

\title{Minutes of meeting \#5}
\author{Group 6}
\date{Tuesday, 2018-02-20 12:15-14:00}

\begin{document}
\maketitle

\section{Attendance}
\begin{tabular}{l l}
    Benjamin Dyhre Bjønnes     & present \\
    Robin el Salim             & present \\
    Sverre Magnus Engø         & absent \\
    Robin Grundvåg             & present \\
    Vegard Itland              & present \\
    Eirik Jørgensen            & present \\
    Loc Tri Le                 & permitted leave (hospital) \\
    Stian Soltvedt             & present
\end{tabular}

\section{Pre-meeting catchup}

\paragraph{Pushing to git}

Previous deliverables were pushed to git.

\paragraph{User manual in separate document}

Due to a misunderstanding, the user manual was incorporated as a part of the product specification, which was corrected during this meeting.

\paragraph{Standardization}

Due to the individuals working separately outside of meetings, documents across the project had different names. The documents were renamed to a consistent naming scheme. Shortly following the group meeting, the folder structure was reorganized in a more logical manner. Efforts were made in standardizing the LaTeX document structure.

\section{Main topic: Tasks 5 and 6}

\paragraph{Retrospective}

A number of good and bad points were addressed by several team members. A document was produced which summarized the points discussed. This document will be further used in subtask \#6.

\paragraph{Presentation}

We will prepare a presentation for next meeting, and will hopefully be able to go through the presentation at that time. The presentation will consist of a manuscript, upon which we will base a powerpoint which will be presented during the official group presentation.

\paragraph{Task division}

We divided the tasks as follows:
\begin{easylist}[itemize]
    # Vegard: Product specification cleanup/standardization
    # Stian: Retrospective document (completed during the meeting)
    # Robin G: Presentation manuscript
    # Benjamin: Presentation powerpoint
\end{easylist}

\section{Meeting review}

\paragraph{What worked?}

All previous deliverables were properly added. Project is starting to come together. We have clearly assigned team members to do the tasks which need to be done by next time.

\paragraph{What didn't work?}

We had a slow start this meeting. Mainly minor decisions were made, perhaps a function of this being a late stage in the project. The group felt particularly low energy, and it was difficult to keep the team on track.

\section{Conclusion}

We discussed some minor yet important details, and divided the required tasks until next meeting. The first iteration is nearing its completion.

\paragraph{Next meeting}

The next meeting will be held in Høyteknologisenteret, in an available group room, on Thursday 2018-02-22 at 14:15-16:00

\end{document}
