\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[left=3.5cm, right=3.5cm]{geometry}
\usepackage[sharp]{easylist}

\title{Minutes of meeting \#6}
\author{Group 6}
\date{Thursday, 2018-02-22 14:15-16:00}

\begin{document}
\maketitle

\section{Attendance}
\begin{tabular}{l l}
    Benjamin Dyhre Bjønnes     & present \\
    Robin el Salim             & present \\
    Sverre Magnus Engø         & permitted leave \\
    Robin Grundvåg             & present \\
    Vegard Itland              & present \\
    Eirik Jørgensen            & present \\
    Loc Tri Le                 & present \\
    Stian Soltvedt             & present
\end{tabular}

\section{Pre-meeting catchup}

\paragraph{Check that everything is in order}

We made sure that all the deliverables required were in place.

\begin{easylist}[itemize]
    # Repo structure: check
    # Sensible commit messages: check
    # Documents in LaTeX: check
    # Everything has a PDF version: check
    # LaTeX of all minutes of meeting: every meeting except 2018-02-22
    # Team plan: check
    # Product specification: check
    # User manual: check
    # Retrospective summary: changes to be made
    # Presentation: today's topic
\end{easylist}

\section{Main topic: Presentation}

\paragraph{Presentation powerpoint}

Benjamin had made a version of the powerpoint, but there is no content yet.

\paragraph{Role distribution, presentation}

\begin{easylist}[itemize]
        # Stian: Intro, group presentation
        # Vegard: Talk about meetings, what we did during them and how they went
        # Robin G: How we worked, communication/tools
        # Benjamin: The good, what we did well, what went smooth
        # Loc: The bad, challenges, and how we fixed them
        # Eirik: Risk assessment - feature creep (feep), time estimation
        # Robin E: Risk assessment - integration issues, competence loss
        # (Sverre: outro)
\end{easylist}

The responsibility for fleshing out their own sections lies with the individual team members.

\subparagraph{"Loss of competence"}

After the group meeting, it came to light that Sverre would have a hard time being able to join us for the presentation due to schedule conflicts. The group will be able to go on without him, but he will talk to the powers that be about it so we can find out how to best sort it out.

\paragraph{Assigning other tasks}

\begin{easylist}[itemize]
    # Vegard: Rename all minutes of meetings to their date, check that product specification contains the content described in task 2
    # Stian: Check that all documents are present (done)
    # Benjamin, Eirik, Loc: Insert text into the presentation
\end{easylist}

\paragraph{Early Monday meeting}

The group decided to hold an off record last-minute meeting on Monday at 8, just before the lecture where the presentations are to be held, in order to go through the presentation and ensure we got it. However, showing up for this meeting is not mandatory, and those who believe they've got their part down perfectly are not required to be there. This will be left to the discretion of the members.

\section{Meeting review}

\paragraph{What worked?}

This was a particularly high-energy meeting with very active participation from all members, and people actively worked on keeping the conversation on track. We made a lot of decisions about the content of the presentation, had a test run to see how it went, and decided roughly what each person should be talking about. The team spirits were very high, and the meeting was by-and-large very enjoyable and productive.

\paragraph{What didn't work?}

Because we lacked a team member, we were not able to go through everyone's role properly. Since the content of the presentation was not yet properly decided, we could not do a final version test run.

\section{Conclusion}

We built the rough structure of the presentation and managed to cough up enough content to do a test run. The presentation file as well as a PDF version needs to be uploaded to the git repo by Friday 2018-02-23, at 16:00 CEST. The presentation must be ready to be held on Monday at 10:15.

\paragraph{Next meeting}

The members who would like to do a test run of the presentation may meet at 08:15 on Monday in order to go through the entire presentation from start to finish to make sure it's all right. This is not a mandatory meeting.

\end{document}

