\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[left=3.5cm, right=3.5cm]{geometry}

\title{Minutes of meeting \#2}
\author{Group 6}
\date{Thursday, 2018-02-08 14:15-16:00}

\begin{document}
\maketitle

\section{Attendance}
\begin{tabular}{l l}
    Benjamin Dyhre Bjønnes     & present \\
    Robin el Salim             & present \\
    Sverre Magnus Engø         & present \\
    Robin Grundvåg             & present \\
    Vegard Itland              & present \\
    Eirik Jørgensen            & present \\
    Loc Tri Le                 & permitted absence \\
    Stian Soltvedt             & present
\end{tabular}

\section{Pre-meeting catchup}

\paragraph{Ongoing tasks}

By default, the responsibility of transcribing the minutes of meeting to LaTeX falls to the documentation manager. A crown has been commissioned for our team leader to lend him an air of authority and foster camaraderie and team spirit within the group. It should be finished by our next meeting.

\paragraph{Git policy}

For the time being, the policy of pushing minutes and other notes to master remains.

\paragraph{Chat group policy}

Anything relevant to the project or the planning of the project shall be acceptable to post in the Facebook chat group.

\paragraph{Meeting agenda}

The team leader and documentation manager have assumed joint responsibility for maintaining an agenda for the next meeting. The other team members may send topics for discussion or things they want to talk about next meeting in the group chat, and it will subsequently be added to the agenda. We hope that the joint responsibility will encourage over-preparation rather than under-preparation, and that the lower activation energy of sending topics over chat compared to maintaining one's own pre-meeting agenda will make it easier for other team members to contribute.

\section{Main topic: Project overview (subtask \#2)}

We went over the higher level description of the product we will create, as well as the delivery requirements for the product specification and the user manual. The team was then divided into two subgroups. One group was responsible for creating a first draft of the user manual, while the other was responsible for the draft of the product specification.

\mbox{}\newline
\noindent
\textbf{NOTE:} These drafts are not yet finalized, and are subject to change.

\paragraph{Product specification}

We produced a short description of the product we intend to make, listed some functional and non-functional requirements, and wrote down some user operations which may be included in the required use case diagram.

\subparagraph{User stories}

User stories were not added, as the required format and contents of these are not entirely clear. We will ask the TA about this during the next meeting.

\paragraph{User manual}

The introduction to the game was written, the rules were outlined, and the ways different pieces can move was illustrated. A list of key features of the game was produced.

\paragraph{Other}

\subparagraph{Scope of product specification}

We intend to ask the TA about the scope of (different sections of) the product specification, as well as clarifications on parts of the task description which we felt were unclear.

\subparagraph{Presentation}

It was suggested that we try to create the presentation described in subtask \#6 in parallel with the other tasks, but no effort has yet been expended in this area.

\subparagraph{Internal team crash course on tools}

Due to the varying level of experience with different tools and skillsets such as the usage of Git, markdown, etc, it was suggested that we hold an internal team course on these topics in order to bring everyone up to speed. When or how this should be done has not been decided.

\subparagraph{Tentative future role assignments}

\mbox{}\newline\newline
\begin{tabular}{l l l}
    Name             & Role            & Comment \\
    \hline
    Robin Grundvåg   & test managers   & responsible for tests during development phase \\
    Robin el Salim   &                 & \\
    Benjamin Bjønnes & diagram masters & responsible for creation of diagrams and other \\
    Eirik Jørgensen  &                 & visual assets during planning phase

\end{tabular}

\subparagraph{Notes for the future}

We wrote down a few notes on topics which may be explored in further detail in future meetings. These notes may find their way to a future agenda, or become ideas or points of reference for future iterations of the project.

\section{Meeting review}

\paragraph{What worked?}

We successfully distributed some of the tasks required to complete the second subtask. Splitting the team up in two subgroups seemed to work well, since it lowered the number of people to communicate with to a more manageable level. We were reasonably prepared for this meeting, due to having written an agenda in advance, which we believe was beneficial to our productivity. Furthermore, all the members were active and contributed to the discussion. Several members spoke up and assumed the responsibility of a particular task.

\paragraph{What didn't work?}

At times we found it difficult to keep the conversation on track, as it sometimes derailed into topics not relevant to the subject at hand. Due to a mixup, the meeting time conflicted with the schedule of one of the members, but this is not expected to become a common occurrence. Some of the things we wanted to discuss were difficult to have a meaningful conversation about without the TA available to clarify important questions.

\section{Conclusion}

We discussed the second subtask of the assignment, and have started to produce some tentative output. We've also more firmly established the responsibilities of the individual team members, both throughout the planning phase and during future iterations, as well as the process of team meetings.

\paragraph{Next meeting} The next meeting will be held in Høyteknologisenteret, group room 205M3, on Tuesday 2018-02-13 at 12:15-14:00

\end{document}
