
\documentclass{article}
\begin{document}
\title{User Manual}
\maketitle
Chess is a game consisting of two players who both have the objective of killing the opponents King before the opponent kills their King. The game ends when the opponent cannot move the King without it being stuck in the next move. This happens when the king is put into check and cannot get out of check. There are only three ways a king can get out of check: move out of the way (though he cannot castle!), block the check with another piece, or capture the piece threatening the king. If a king cannot escape checkmate, then the game is over.The winning player will then exclaim “Check mate”. The losing player then responds by “I’m not your mate, friend.” or “Good game” depending on nationality. 
\\

Chess is a game for all ages. It’s been around for 1500 years, which makes it one of the oldest games in the world. Chess is a fun and challenging game for all age groups, however understanding how the pieces move might require the cognitive level of an average 5 year old or above. Chess is not a mastered game, and thus you can always improve your game. You can always find a challenging match in chess, and world champion cannot win every game. In the first 4 moves alone, there is a total of 319 billion possible outcomes.
\\

The player with the white pieces starts the game by taking the first move.
The two ways to end a game of chess is either by checkmate, or with a draw.
\\

Sometimes chess games do not end with a winner, but with a draw. There are 5 reasons why a chess game may end in a draw:
The position reaches a stalemate where it is one player's turn to move, but his king is NOT in check and yet he does not have another legal move
The players may simply agree to a draw and stop playing
There are not enough pieces on the board to force a checkmate (example: a king and a bishop vs.a king)
A player declares a draw if the same exact position is repeated three times (though not necessarily three times in a row)
Fifty consecutive moves have been played where neither player has moved a pawn or captured a piece.

\end{document}